\include{preamble}
\subtitle{Assignment 3: Parsing}
\begin{document}

\makefancytitle

\section{Left recursion}

\cc{Same as in 2017.}

Consider the following grammar.
\begin{lstlisting}
<sentence> ::= <words>
<words> ::= <words><word> | <word>
\end{lstlisting}

Do the following tasks.
\begin{enumerate}
\item Remove the left recursion.
\item Why are left recursions bad? For what type of parsers? Keep the answer short and precise.
\end{enumerate}


\section{Extending the grammar}

\cc{Same as in 2017.}

Extend the grammar from Exercise 1 so it can support questions (sentences terminated with a question mark), exclamations (sentences terminated with a exclamation mark), complex sentences (parts are divided by a comma), and the notion that the first word of a sentence must begin with a capital letter. Also, any other word in the sentence can begin with a capital letter. Assume that \texttt{<capitalWord>} is a word with a capital first letter.

Extra task (not graded): Write regular expressions for \texttt{<capitalWord>} and \texttt{<word>}.


\section{Parsing mathematical expressions in reverse Polish notation}

Write a grammar for parsing mathematical expressions in Reverse Polish Notation\footnote{\url{https://en.wikipedia.org/wiki/Reverse_Polish_notation}} (RPN).
Your grammar should be able to parse expresions that include digits the binary operators * (multiplication), - (subtraction), + (addition), / (division), as well as the unary operators N (negation) and ! (factorial).

Valid expressions:
\begin{itemize}
\item 3 4 +
\item 10 2 + ! 3 4 + * 5 6 * /
\item 2 ! 3 ! +
\item 12 N
\item 12 13 -
\item 1 2 N - ! N
\end{itemize}

Invalid expressions:
\begin{itemize}
\item 3 + 4
\item + 1 2
\item 1 +
\item 5 -
\end{itemize}

Extra task (not graded): Ensure that your grammar does not contain any left recursion.

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
