\include{preamble}
\subtitle{Assignment 2: Lexical Analysis}
\begin{document}

\makefancytitle


\section{NFA and DFA}

Consider the following regular expression.
\[
  a^* \left( bc \mid de \right) b^*c
\]

Do the following tasks:
\begin{enumerate}
\item Draw a non-deterministic finite automaton (NFA) for the expression, and
\item transform it to a deterministic finite automaton (DFA).
\end{enumerate}


\section{Expressiveness}

Explain why there are no regular expressions which can express the language $a^n b^n$, where $n$ is any positive number.


\section{Writing Regular Expressions (1)}

Write a regular expression that matches \emph{banana, bananas, ananas, ananana, anna}, but not \emph{baanana, anannass, anaa, ans}.

Make the expression as short as possible. \cc{b?((an+)+a)s?}


\section{Writing Regular Expressions (2)}

Write a regular expression for non-negative integers with a time unit suffix.
The possible suffixes are \enquote{ms} (milliseconds), \enquote{s} (seconds), \enquote{m} (minutes), \enquote{h} (hours), and \enquote{d} (days).
Ensure that only integers that make sense are matched.
For example, \enquote{25h} should not be possible, nor should \enquote{1200ms} be a match (instead, they should be written as \enquote{1d 1h} and \enquote{1s 200ms} respectively).
Multiple units can be combined using spaces (but do not have to be in a specific order).

Write a single expression. Examples are as follows:

\begin{description}
\item[Matches] 256ms, 5s, 32m, 16h, 4d, \enquote{1d 1h}, \enquote{2h 1d 3s}.
\item[No matches] 05ms, 10e, -2h, 100s, 25h.
\end{description}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
