\include{preamble}

\subtitle{Semester project}

\begin{document}

\makefancytitle

\setcounter{section}{1}
\section{Type Checker} 

In the second part of the semester project, you will implement a type checker for Mini Java. To pass the exercise, do the following tasks.

\begin{itemize} 

\item Implement static type checker for Mini Java.

\item The provided test suite specifies the type checker rules.
  Use it to ensure that your implementation works as expected.
  We will use these test cases to evaluate your type checker.
  However, we may also use additional tests that check for different scenarios, so you may want to implement your own additional test cases.
  You are not allowed to modify the existing test cases.

\item Your type checker should reuse the front end implemented in the first part of the project.
  You are free to improve and modify the code from the first part, as long as it passes the test suites from both project parts.

\item Import the provided test suite into your eclipse project.

\item You have time until \todo{NN April 2017, 10:00} to complete this part of the project.

\item Push your solution (the Eclipse project, including the parts provided by us) into the your Bitbucket repository. Share the repository with the user \todo{\emph{scg-uko} update user}. 

\item You are not allowed to use other people’s work.
  All parts of the project solution must be your own work.

\end{itemize}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End: